---
title: "Study_area"
format:
  html:
    self-contained: true
    link-external-icon: true
    link-external-newwindow: true
toc: true
editor: visual
---

# Introduction

The Hudson-James Bay lowlands (HJBL) is located in the Mushkegowuk territory including various First nation communities: Attawapiskat First Nation, Taykwa Tagamou Nation, Kashechewan First Nation, Fort Albany First Nation, Moose Cree First Nation, Chapleau Cree First Nation, Missanabie Cree First Nation, and Weenusk First Nation (see [Mushkegouk Council](https://mushkegowuk.ca/)). It is located in northeast Canada, known also as the [Hudson Bay Plains ecozone](http://www.ecozones.ca/english/zone/index.html) in the provinces on Ontario, Manitoba and Quebec.

```{r, echo = FALSE, warning=FALSE, message=FALSE, include = FALSE}

source("mapsR.R")


```

The interactive map below some important thematic layers:

```{r, echo=FALSE, warning=FALSE, message=FALSE}


#library(shiny)
library(magrittr)
library(leaflet)


area_map=leaflet() %>%
           setView(lng = -91, lat = 60, zoom = 3)%>%
   
  addScaleBar(position = 'bottomleft') %>%
  
# Background World map
  addProviderTiles("Esri.WorldImagery",'https://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}') %>%

# Canada
  addPolygons(data =  Canada$geometry,
              weight =  2,
              color = "grey",
              label = Canada$juri_en,
              group = "Canada"
            #   highlightOptions = highlightOptions(
             #   weight = 1,
             #   bringToFront = T,
             #   color = "grey",
            #    fillOpacity = 0.1)
              )%>%

# Study area
  addPolygons(data=study_area,
              weight=3,
              color =  "white",
              fillColor = "white",
              fillOpacity =  0.01,
              label=study_area$ECOZONE_NAME_EN,
              group = "Study_area",
              highlightOptions = highlightOptions(
                weight = 1,
                bringToFront = T,
                color = "white",
                fillOpacity = 0.1))%>%
  
# Treaties
 # addPolygons(data=treaties,
    #          weight=0.4,
     #         fillColor = rev(topo.colors(n=length(treaties$Name))),
     #         color = "white",
     #         label = treaties$Name,
      #        group = "Treaties",
      #        fillOpacity = 0.1,
      #        highlightOptions = highlightOptions(
       #         weight = 5,
       #         color = "white",
        #        fillOpacity = 0.3))%>%
  
# Territories
  addPolygons(data=territories_area,
              weight=0.4,
              fillColor = topo.colors(n=length(territories_area$Name)),
              color =  "white",
              label =  territories_area$Name,
              group = "Territories",
              fillOpacity = 0.1,
              highlightOptions = highlightOptions(
                weight = 5,
                color = "white",
                fillOpacity = 0.3))%>%
 
# Ecozones
 # addPolygons(data=ecozones_can,
    #          weight=3,
   #           color =  rainbow(n=length(ecozones_can$ECOZONE_NAME_EN)),
    #          label=ecozones_can$ECOZONE_NAME_EN,
    #          group = "Ecozones")%>%

# Municipalities
  addCircleMarkers(st_coordinates(municipalities_area)[,1],
                        st_coordinates(municipalities_area)[,2],
                         fillColor="white",
                         fillOpacity = 0.8,
                         weight=1,
                         label = municipalities_area$GEONAME,
                         group= "Municipalities",
                         radius = 4)%>%
  
# Protected_Areas
  addPolygons(data=protected_areas,
               weight=1.3,
               color = "#CCCC00",
               fillColor = "#CCCC00",
               label=protected_areas$NAME,
               group = "Protected_Areas",
               fillOpacity = 0.01,
               highlightOptions = highlightOptions(
                  weight = 0.1,
                  color = "white",
                  fillColor = rainbow(length(protected_areas$NAME)),
                  fillOpacity = 0.3)
  )
  
  


  
 
area_map = area_map  %>%
   
# ADDING TOOLS -------------
    
  # add a map scalebar
    addScaleBar(position = 'bottomleft') %>%
              
  # add measurement tool
    addMeasure(primaryLengthUnit = "kilometers",
               secondaryLengthUnit = 'miles',
               primaryAreaUnit = "hectares",
               secondaryAreaUnit="acres",
               position = 'topleft') 

  area_map = area_map %>%
    
  # Adding layer control
          addLayersControl(options = layersControlOptions(collapsed = T),
                             position ="topleft",
                           baseGroups = "Canada",
                             overlayGroups = c( "Protected_Areas",
                                               "Municipalities",
                                               # "Ecozones",
                                                "Territories",
                                              #  "Treaties",
                                                 "Study_area")) %>%
            hideGroup(c(#"Ecozones",
                       # "Treaties",
                        "Municipalities",
                        "Protected_Areas",
                        "Territories")
                    )
          

area_map
```

Selected features from these sources:

-   Canada boundaries: [open.canada.ca](https://open.canada.ca/data/en/dataset/85efc01b-163f-ebba-2378-c43eadfb3b3f/resource/15f721b1-ed0f-4883-80c3-8e3d9bec20d6?inner_span=True)

-   Treaties and territories: [Native Land Digital](https://native-land.ca/)

-   Ecozones (study area): [National Ecological Framework](https://agriculture.canada.ca/atlas/data_donnees/nationalEcologicalFramework/data_donnees/)

-   Protected areas (raw data): [World Database on Protected Areas (WDPA)](https://www.protectedplanet.net/en), using R interface [wdpar](https://cran.r-project.org/web/packages/wdpar/index.html).
